Influence of Connectivity on Dung Beetle Communities

### 2025-06-17 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
discisuition

Species-patch interactions indicated indicated species specific responses to treatments. In matrix plots, the positive effect on abundance was reduced for all other species (e.g., cvig × Matrix $\beta$ = –0.59, p < 0.001). _Ateuchus lecontei_ and _Phanaeus igneus_ showed increased abundance in rectangle patches relative to expectations ($\beta$ = 0.40 and 0.47, respectively; p < 0.05). Random effects indicated moderate variability among blocks (standard deviation of intercept = 0.51).

@@

We also observed that patch effects were not equally proportional for all species. The abundances of all dominant species were positively influenced by matrix habitat, but _Aphoidius alloblackburneus_ responded more positively than any other species. _Phanaeus igneus_ and _Ateuchus lecontei_

@@

@@

We thank the USDA Forest Service for maintaining experimental landscapes and assisting in getting established at the site. I also wanted to specificallly thank Thomas Smith for his help in data collection, Sara Escobar-Chena for her help in processing and data entry.

>>>>

Species-patch interactions indicated indicated species specific responses to treatments. In matrix plots, the positive effect on abundance was reduced for all other species (e.g., cvig × Matrix $\beta$ = –0.59, p < 0.001). _Ateuchus lecontei_ and _Phanaeus igneus_ showed increased effect on abundance in rectangle patches relative to expectations ($\beta$ = 0.40 and 0.47, respectively; p < 0.05). Random effects indicated moderate variability among blocks (standard deviation of intercept = 0.51).

@@

We also observed that patch effects were not equally proportional for all species. The abundances of all dominant species were positively influenced by matrix habitat, but _Aphoidius alloblackburneus_ responded more positively than any other species. _Phanaeus igneus_ and _Ateuchus lecontei_ also had higher positive effects in rectangle patches. .

@@

 notes that are important for discussion

 - habitat preference and seasonality (conover 2019, nealis 1977)
 - habitat again but  only part of variation form habitat specifically aphodius also phenology(roslin 2001)
 - spatial scales (roslin 2000)
 - morphology (ospina 2018)
 - functionality especially gas emissions (slade 2016)
 - species id and funcitonality (slade 2017)
 - faovored species dominating in fragments (resasco 2014)
 - wind direction in corridors (damschen 2014)

@@

We thank the USDA Forest Service for maintaining experimental landscapes and assisting in getting established at the site. I also wanted to specifically thank Thomas Smith for his help in data collection, Sara Escobar-Chena for her help in processing and data entry.
